---
title: "Coca-cola Group, Barcelona Fri 28 - Sun 30 June 2019"
output: 
  flexdashboard::flex_dashboard:
    logo: logo.png
    theme: sandstone
---

DaybyDay {.storyboard}
===================================== 

### _**Day 1- Friday, June 28th - 2019**_ {data-commentary-width=150}


<br><br>

```{r echo = FALSE, warning=FALSE, message=FALSE}

library(dplyr)
library(knitr)
library(kableExtra)
library(plotly)
library(formattable)
library(readxl)

program <- read_excel("program.xlsx", sheet = "day1")
program$finish[is.na(program$finish)] <- ""
program$notes[is.na(program$notes)] <- ""
program$notes[is.na(program$notes)] <- ""

table_style <- function(x){
  x %>% kable(format = "html", escape = F) %>% kable_styling(fixed_thead = T,bootstrap_options = c("striped","condensed","hover","responsive")) %>%
row_spec(0, bold = T, color = "white", background = "black") 
}

program %>% select(1:6) %>% 
  mutate(
  owner = cell_spec(owner,
  "html", color = ifelse(owner == "CUTTING","#ee7600", "blue"))) %>% table_style()


```

*** 

click activity for menu information
click owner for phone contacts


### Day 2- Saturday, June 29th - 2019 {data-commentary-width=200}

```{r}

```

*** 

comments

Accommodation 
===================================== 

_**Rooming List**_ 
--------------------------------------

### Hotel Palas

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(DT)
library(readxl)
library(lubridate)
library(dplyr)
library(chron)

rooming <- read_excel("rooming.xlsx", sheet = "rooming", 
           col_types = c("text", "text", "text", "date", "date","text","text","text"))

rooming <- rooming %>% arrange(last)
rooming$chkin <- ymd(rooming$chkin)
rooming$chkout <- ymd(rooming$chkout)
rooming$room_type <- factor(rooming$room_type)

trnsfin <- read_excel("rooming.xlsx", sheet = "trnsfin",
           col_types = c("text","text","text","date","date","text"))

trnsfin$arr_time <- times(format(trnsfin$arr_time,"%H:%M:%S"))
trnsfin$trnsf_in <- as.Date(trnsfin$trnsf_in) %>% format("%Y-%m-%d")

trnsfout <- read_excel("rooming.xlsx", sheet = "trnsfout",
           col_types = c("text","text","text","date","date","text","date","text"))

trnsfout$trnsfout_time <- times(format(trnsfout$trnsfout_time,"%H:%M:%S"))
trnsfout$pick_up <- times(format(trnsfout$pick_up,"%H:%M:%S"))
trnsfout$trnsf_out <- as.Date(trnsfout$trnsf_out) %>% format("%Y-%m-%d")


total <- merge(rooming,trnsfin, by = c("first","last","country"), all = TRUE)
total_in_out <- merge(total,trnsfout, by = c("first","last","country"),
                      all = TRUE)

total_in_out_table <- total_in_out %>% arrange(last) %>% 
  select(first,last,room_type,chkin,trnsf_in,chkout,trnsf_out)

total_in_out_table$colors <- with(total_in_out_table, 
  ifelse(trnsf_in >= chkin,"lightgreen","red"))

datatable(total_in_out_table,
          options = list(pageLength = 100,
            columnDefs = list(
              list(
                visible = FALSE, targets = 8)))) %>% 
              formatStyle(c("trnsf_in","chkin"), `text-align` = 'center', valueColumns = "colors", backgroundColor = JS("value"))


```


Rooming List charts 
===================================== 

_**Rooming chart**_ {data-width=334}
----------------------------------------

### 1st 

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)

rows1 <- round(nrow(rooming)/3, digits = 0)
rooming1 <- rooming[1:rows1,]

rooming_chart <- function(x){
  x %>% ggplot() + geom_segment(aes(x = factor(last, levels = rev(levels(factor(last)))), 
  xend = factor(last, levels = rev(levels(factor(last)))),
  y = chkin, yend = chkout ),
  color = "grey") + 
geom_point( aes(x=last, y=chkin, first = first, allergies=allergies, room_type=room_type), color = rgb(0.2,0.7,0.1,0.5), size=3 )+
geom_point(aes(x=last, y=chkout, first = first, remarks = remarks), color=rgb(0.7,0.2,0.1,0.5), size=3 )+         
 coord_flip() +
 theme_light() +
 theme(legend.position = "none",
 panel.border = element_blank())+ xlab("")+ ylab("check in/out")
  }

ggplotly(rooming_chart(rooming1), tooltip = c("first", "room_type","allergies", "remarks"))
 
```


_**Rooming chart**_ {data-width=333}
----------------------------------------

### 2nd 

```{r echo=FALSE, warning=FALSE, message=FALSE}


rows2 <- round(nrow(rooming)*2/3, digits = 0)
rooming2 <- rooming[(rows1+1):rows2,]

ggplotly(rooming_chart(rooming2), tooltip = c("first","room_type","allergies","remarks"))
 
```


_**Rooming chart**_ {data-width=333}
----------------------------------------

### 3rd 

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)

rows3 <- nrow(rooming)
rooming3 <- rooming[(rows2+1):rows3,]

ggplotly(rooming_chart(rooming3), tooltip = c("first","room_type","allergies","remarks"))
 
```


Budget {data-navmenu="financials"}
===================================== 


```{r echo=FALSE, warning=FALSE, message=FALSE}
tables <- function(x){

x %>% select(1:5) %>% mutate(total = paste("EUR", format(round(total, 2L),nsmall = 2,big.mark = ","))) %>% 
  kable(
   format = "html", escape = F) %>% kable_styling(fixed_thead =   T,bootstrap_options = c("striped","condensed","hover","responsive")) %>%
row_spec(0, bold = T, color = "white", background = "black")  %>% 
  column_spec(1, width = "8em") %>% 
  column_spec(5,bold = TRUE, width = "8em")}
```


_**Coca-cola group**_ {data-width=850}
-------------------------------------------

### Budget as of May 25, 2019

<br><br>

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(DT)
library(readxl)
library(lubridate)
library(dplyr)
library(chron)
library(kableExtra)
library(scales)
library(tidyverse)

budget <- read_excel("rooming.xlsx", sheet = "bud") 
budget <- sapply(budget, as.character)
budget[is.na(budget)] <- ""
budget <- data.frame(budget, stringsAsFactors = FALSE)
class(budget$bud_units) <- "numeric"
class(budget$bud_cost) <- "numeric"
class(budget$bud_total) <- "numeric"

names(budget) <- c("date","description","units","unit cost","total","category")


budget[nrow(budget),] <- c("","","<strong>Total</strong>","",sum(budget$total),"")

class(budget$total) <- "numeric"

tables(budget)

```

_**Coca-cola group**_{data-width=150}
-------------------------------------------

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(flexdashboard)

budget <- budget[-nrow(budget),]

bud_transfers <- budget %>% filter(category == "transfer") %>% summarise(total= sum(total)) %>% prettyNum(big.mark = ",")

bud_activity <- budget %>% filter(category == "activity") %>% summarise(total= sum(total))%>% prettyNum(big.mark = ",")

bud_hotel <- budget %>% filter(category == "hotel") %>% summarise(total = sum(total))%>% prettyNum(big.mark = ",")

bud_restaurant <- budget %>% filter(category == "restaurant") %>%  summarise(total = sum(total)) %>% prettyNum(big.mark = ",")

bud_audiovisuals <- budget %>% filter(category == "audiovisuals") %>%  summarise(total = sum(total)) %>% prettyNum(big.mark = ",")

```

<br>

### hotel

```{r echo=FALSE, warning=FALSE, message=FALSE}

valueBox(bud_hotel, 
         icon = "fa-h-square", 
         caption = "Euros in Hotel",
         color = "#fcffc2")
```


### activities

```{r echo=FALSE, warning=FALSE, message=FALSE}

valueBox(bud_activity, 
         icon = "fa-walking", 
         caption = "Euros in activities",
         color = "#b6fcd5")
```


### transfers

```{r echo=FALSE, message=FALSE, warning=FALSE}

valueBox(bud_transfers, icon = "fa-shuttle-van",
         caption = "Euros in transfers",
         color = "#c6e2ff")

```

### restaurants

```{r echo=FALSE, warning=FALSE, message=FALSE}

valueBox(bud_restaurant, 
         icon = "fa-utensils", 
         caption = "Euros in offsite restaurants",
         color = "#fdc9d9")
```


### Audiovisuals

```{r echo=FALSE, warning=FALSE, message=FALSE}

valueBox(bud_audiovisuals, 
         icon = "fa-fast-forward", 
         caption = "Euros in Audiovisuals",
         color = "#b6a3ea")
```


Proforma {data-navmenu="financials"}
===================================== 


_**Coca-cola group**_ {data-width=850}
-------------------------------------------

### Budget as of May 25, 2019

<br>

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(DT)
library(readxl)
library(lubridate)
library(dplyr)
library(chron)
library(kableExtra)
library(scales)
library(tidyverse)

proforma <- read_excel("rooming.xlsx", sheet = "prof") 
proforma <- sapply(proforma, as.character)
proforma[is.na(proforma)] <- ""
proforma <- data.frame(proforma, stringsAsFactors = FALSE)
class(proforma$prof_units) <- "numeric"
class(proforma$prof_cost) <- "numeric"
class(proforma$prof_total) <- "numeric"
names(proforma) <- c("date","description","units","unit cost","total","category")


proforma[nrow(proforma),] <- c("","","<strong>Total</strong>","",sum(proforma$total),"")

class(proforma$total) <- "numeric"

tables(proforma)


```

_**Coca-cola group**_ {data-width=150}
-------------------------------------------

<br><br>


### total proforma

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(dplyr)
library(flexdashboard)

dip <- read_excel("rooming.xlsx", sheet = "dip") 
dip$amount <- as.numeric(dip$amount)
dip_sum <- dip %>% group_by(paid) %>% summarise(sum = sum(amount)) 

total <- sum(dip_sum$sum)

total %>% prettyNum(big.mark = ",") %>% 
valueBox(
         icon = "fa-euro-sign", 
         caption = "Total requested",
         color = "#ffa500")
```


### _**Total paid %**_

```{r echo=FALSE, message=FALSE, warning=FALSE}

paid_dip <- dip_sum$sum[dip_sum$paid == "yes"] 

gauge(100*paid_dip/total, min = 0, max = 100, symbol = '%', gaugeSectors(colors = "yellow"),label = paste0("Total paid ", paid_dip," "))

```


### _**Summary table %**_

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(formattable)
library(readxl)

dip <- read_excel("rooming.xlsx", sheet = "dip")
dip$paid <- ifelse(dip$paid == "yes",TRUE,FALSE)
formattable(dip, list(paid = formatter("span",
      style = x ~ style(color = ifelse(x, "green", "red")),
      x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No")))))
            
```

